% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\author{}
\date{}
\begin{document}


The replication package is deposited under DOI \texttt{xyz}.

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.0500}}
  >{\centering\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.1500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 4\tabcolsep) * \real{0.8000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
Code
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Meaning
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Data Statement
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
A & Available & Data and code for this paper are available in the above
deposit. They were checked by the Journal for their ability to reproduce
the results presented in the paper. \\
S & Simulation & The authors were granted an exemption to publish their
data because access is restricted. However, the authors provided a
simulated or synthetic dataset that allowed the Journal to run their
code. The synthetic/simulated data and code are available in the above
deposit. They were checked for their ability to generate all tables and
figures in the paper. However, the synthetic/simulated data are not
designed to reproduce the same results. \\
T & Temporary & The authors were granted an exemption to publish their
data because access is restricted. However, the authors provided the
Journal with temporary access to the data, which allowed the Journal to
run their code. Code and unrestricted data are available in the above
deposit. Data and code were checked by the Journal for their ability to
reproduce the results presented in the paper. \\
P1 & Partial 1 & Given the highly demanding nature of the algorithms,
the reproducibility checks were run on a simplified version of the code,
which is also available in the deposit. {[}which is to be added right
after the end of any of the previous three statements{]}. \\
P2 & Partial 2 & Given the highly demanding nature of the algorithms,
the reproducibility checks were performed on a subset or results only.
Those are clearly indicated in the accompanying README file of the
replication package. {[}which is to be added right after the end of any
of the previous three statements{]}. \\
A;T & Available, Temporary & Data and code for this paper are available
in the above deposit. They were checked by the Journal for their ability
to reproduce the results presented in the paper. The authors were
granted an exemption to publish parts of their data because access to
these data is restricted. However, the authors provided the Journal with
temporary access to the data, which enabled the Journal to check
reproducibility of results. Code for all parts of the paper and
unrestricted data are available in the above deposit. \\
A;S & Available, Simulation & Data and code for this paper are available
in the above deposit. They were checked by the Journal for their ability
to reproduce the results presented in the paper. The authors were
granted an exemption to publish parts of their data because access to
these data is restricted. However, the authors provided the Journal
provided a simulated or synthetic dataset, which enabled the Journal to
run the code. Code for all parts of the paper and unrestricted data are
available in the above deposit. They were checked for their ability to
generate all tables and figures in the paper, however the
synthetic/simulated data are not designed to reproduce the same
results. \\
A;T;S & Available, Temporary, Simulation & Data and code for this paper
are available in the above deposit. They were checked by the Journal for
their ability to reproduce the results presented in the paper. The
authors were granted an exemption to publish parts of their data because
access to these data is restricted. However, the authors provided the
Journal with temporary access to the parts of the restricted data, which
enabled the Journal to check reproducibility of results. Other parts of
the data remained inaccessibel to the Journal, and the authors provided
a simulated or synthetic dataset, which enabled the Journal to run the
code. Code for all parts of the paper and unrestricted data are
available in the above deposit. They were checked for their ability to
generate all tables and figures in the paper, however the
synthetic/simulated data are not designed to reproduce the same
results. \\
\end{longtable}




\end{document}
